Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-16 article/article.tex
Commit 2024-05-16 19:19

@@

To create a look-up table that aligns with our dataset, we applied some
adjustments. To account for the Sun's variability, in our one-minute GHI
measurements, we adapted each modeled value by scaling the\\
model's input spectrum integral, to the corresponding total solar
irradiance (TSI) provided by NOAA \citep{Coddington2005}.\\
Also, we applied the effect of the Earth -- Sun distance on the
irradiance, by using the distance calculated by the Astropy
\citep{AstropyCollaboration2022} software library. As needed, we
interpolate the resulting irradiances to the exact SZA of our
measurements. For each period of the year, we used the appropriate
atmospheric profile (afglms or afglmw). Finally, we calculated the clear
sky irradiance value at the horizontal plane. Thus, we were able to
emulate different atmospheric condition and levels of atmospheric
clearness for the climatological conditions of the site. With this
method, the modeled clear sky irradiances can be directly compared to
each measured one-minute value of GHI, for different conditions of
atmospheric clearness.

>>>>

\hypertarget{climatology-of-clear-sky-irradiance}{%
\subsubsection{Climatology of clear sky
irradiance}\label{climatology-of-clear-sky-irradiance}}

@@

To create a look-up table, that aligns with our dataset, we applied some
adjustments. To account for the Sun's variability, in our one-minute GHI
measurements, we adapted each modeled value by scaling the model's input
spectrum integral, to the corresponding total solar irradiance (TSI)
provided by NOAA \citep{Coddington2005}. Also, we account for the effect
of the Earth -- Sun distance on the irradiance, by using the distance
calculated by the Astropy \citep{AstropyCollaboration2022} software
library. As needed, we interpolate the resulting irradiances to the
exact SZA of our measurements. For each period of the year, we used the
appropriate atmospheric profile (afglms or afglmw). Finally, we
calculated the clear sky irradiance value at the horizontal plane. Thus,
we were able to emulate different atmospheric condition and levels of
atmospheric clearness for the climatological conditions of the site.
With this method, the modeled clear sky irradiances can be directly
compared to each measured one-minute value of GHI, for different
conditions of atmospheric clearness.

\hypertarget{long-term-change-of-clear-sky-irradiance}{%
\subsubsection{Long term change of clear sky
irradiance}\label{long-term-change-of-clear-sky-irradiance}}

The above clear sky reference values are not enough to describe the long
term variation due to the changes of the atmospheric constituents. As
observed by \citet{Natsis2023}, there is long term brightening effect,
over Thessaloniki for the studied period. In order to better describe
this change, we used, estimations of AOD change derived from two
sources. For 1993 -- 2005, \citet{Kazadzis2007} have found a change of
\(-3.8\,\%\) per year at AOD on \(340\) nm, using a Brewer
spectrophotometer. For 2005 to 2023, we derived the trend from the
available AERONET data.

To create a unified trend for the long term change of the clear sky
irradiance, we sim simulated
